---
title: "MSDM Odoo Website Analytics"
subtitle: "IBM 6530 — Group 4 Final Presentation"
author:
  - "Min Gong"
  - "Jeffrey Hsu"
  - "Emily Kuo"
  - "Eunice Won"
  - "Ceren Unal"
date: today

format:
  revealjs:
    theme: moon
    transition: slide
    slide-number: true
    controls: true
    navigation-mode: linear
    auto-stretch: true
    preview-links: auto
    chalkboard: false
    menu: false
    code-fold: true
    self-contained: true
    scrollable: true
    fig-width: 8
    fig-height: 4.5
    logo: ""
    footer: "IBM 6530 | Group 4 | MSDM Odoo Analytics"
    include-in-header:
      text: |
        <div id="top-hover-zone"></div>
        <div id="top-nav">
          <a href="../index.html">Home</a>
          <a href="../marketing-analytics.html">Marketing Analytics</a>
          <a href="../digital-marketing.html">Digital Marketing</a>
          <a href="../resume.html">Résumé</a>

          <div class="dropdown">
            <span>Website Traffic Analytics ▾</span>
            <div class="dropdown-content">
              <a href="../website-traffic-analytics.html">Website Traffic Project Report</a>
              <a href="../odoo-presentation.html">Revealjs Presentation</a>
            </div>
          </div>
        </div>

execute:
  warning: false
  message: false
  echo: false
  cache: false
---

```{r setup}
library(arrow)
library(dplyr)
library(ggplot2)
library(scales)
library(forcats)
library(stringr)
library(tidyr)
library(fs)
library(here)
library(readr)
library(ggrepel)

# ── GA4 snapshot ───────────────────────────────────────────────────────────────
DATA_DIR     <- here::here("data")
PARQUET_DIR  <- fs::path(DATA_DIR, "msdm_snapshot", "events_flat")
PARQUET_FILE <- fs::path(PARQUET_DIR, "events_snapshot.parquet")
CSV_PATH     <- fs::path(DATA_DIR, "events_snapshot.csv")

if (!fs::file_exists(PARQUET_FILE)) {
  fs::dir_create(PARQUET_DIR)
  arrow::write_parquet(
    readr::read_csv(CSV_PATH, show_col_types = FALSE),
    PARQUET_FILE
  )
}

ds <- arrow::open_dataset(PARQUET_DIR) |> dplyr::collect()

# Traffic medium
traffic_summary <- ds |>
  filter(event_name == "page_view") |>
  mutate(
    medium_clean = case_when(
      is.na(traffic_medium)      ~ "(not set)",
      traffic_medium == "(none)" ~ "direct",
      TRUE                       ~ traffic_medium
    )
  ) |>
  count(medium_clean, name = "page_views") |>
  arrange(desc(page_views))

# Device
device_summary <- ds |>
  filter(!is.na(device_category)) |>
  group_by(device_category) |>
  summarise(
    n_events       = n(),
    n_unique_users = n_distinct(user_pseudo_id)
  ) |>
  arrange(desc(n_events)) |>
  mutate(pct_events = n_events / sum(n_events) * 100)

# ── Attribution dataset ────────────────────────────────────────────────────────
attr_raw      <- readr::read_csv(here::here("data", "attribution_dataset.csv"),
                                 show_col_types = FALSE)
channel_cols  <- grep("^channel", names(attr_raw), value = TRUE)
channels_list <- c("Direct", "Email", "Organic", "Paid Search", "Paid Social", "Referral")

`%||%` <- function(a, b) if (!is.null(a)) a else b

# Last-Touch
converters <- attr_raw |> dplyr::filter(user_purchase == 1)
last_touch_attr <- converters |>
  rowwise() |>
  mutate(last_ch = {
    v <- c_across(all_of(channel_cols)); v <- v[!is.na(v)]
    if (length(v) > 0) tail(v, 1) else NA_character_
  }) |>
  ungroup() |> filter(!is.na(last_ch)) |>
  count(last_ch, name = "credit") |>
  mutate(Last_Touch = round(credit / sum(credit) * 100, 1)) |>
  rename(Channel = last_ch) |> select(Channel, Last_Touch)

# First-Touch
first_touch_attr <- converters |>
  rowwise() |>
  mutate(first_ch = {
    v <- c_across(all_of(channel_cols)); v <- v[!is.na(v)]
    if (length(v) > 0) v[1] else NA_character_
  }) |>
  ungroup() |> filter(!is.na(first_ch)) |>
  count(first_ch, name = "credit") |>
  mutate(First_Touch = round(credit / sum(credit) * 100, 1)) |>
  rename(Channel = first_ch) |> select(Channel, First_Touch)

# Markov (absorbing chain)
build_transitions <- function(df, channel_cols) {
  trans <- list()
  for (i in seq_len(nrow(df))) {
    path <- unlist(df[i, channel_cols]); path <- path[!is.na(path)]
    if (length(path) == 0) next
    outcome <- if (df$user_purchase[i] == 1) "conversion" else "null"
    from <- "start"; to <- path[1]
    trans[[from]][[to]] <- (trans[[from]][[to]] %||% 0) + 1
    if (length(path) > 1) {
      for (j in seq_len(length(path) - 1)) {
        from <- path[j]; to <- path[j + 1]
        trans[[from]][[to]] <- (trans[[from]][[to]] %||% 0) + 1
      }
    }
    from <- tail(path, 1)
    trans[[from]][[outcome]] <- (trans[[from]][[outcome]] %||% 0) + 1
  }
  trans
}

trans_counts <- build_transitions(attr_raw, channel_cols)
trans_prob   <- lapply(trans_counts, function(x) {
  tot <- sum(unlist(x)); lapply(x, function(v) v / tot)
})

all_transient <- c(channels_list, "start")
absorbing     <- c("conversion", "null")
n_t           <- length(all_transient)

Q <- matrix(0, n_t, n_t, dimnames = list(all_transient, all_transient))
R <- matrix(0, n_t, 2,   dimnames = list(all_transient, absorbing))
for (s in all_transient) {
  probs <- trans_prob[[s]]; if (is.null(probs)) next
  for (t in names(probs)) {
    p <- probs[[t]]
    if (t %in% all_transient) Q[s, t] <- p else if (t %in% absorbing) R[s, t] <- p
  }
}
N_mat         <- solve(diag(n_t) - Q)
B_mat         <- N_mat %*% R
baseline_conv <- B_mat["start", "conversion"]

removal_effects <- sapply(channels_list, function(ch) {
  Q2 <- Q; R2 <- R
  for (s in all_transient) {
    if (Q2[s, ch] > 0) { R2[s, "null"] <- R2[s, "null"] + Q2[s, ch]; Q2[s, ch] <- 0 }
  }
  Q2[ch, ] <- 0; R2[ch, ] <- c(0, 1)
  tryCatch({
    N2 <- solve(diag(n_t) - Q2); B2 <- N2 %*% R2
    max(0, baseline_conv - B2["start", "conversion"])
  }, error = function(e) 0)
})

markov_attr <- data.frame(
  Channel = names(removal_effects),
  Markov  = round(removal_effects / sum(removal_effects) * 100, 1)
)

# Combined comparison
comparison <- last_touch_attr |>
  full_join(first_touch_attr, by = "Channel") |>
  full_join(markov_attr,      by = "Channel") |>
  arrange(desc(Last_Touch))
```

## Business Problem {background-color="#2c3e50"}

::::: columns
::: {.column width="55%"}
**Client:** MSDM Program — Odoo Website

**Core Questions:**

-   Where is traffic coming from?
-   Who is visiting & on what device?
-   Which channels drive conversions?
-   Where should budget be focused?
:::

::: {.column width="45%"}
**Why it matters:**

The MSDM program needs to understand its digital presence to make smarter decisions about outreach and marketing investment.

Standard last-touch reporting tells an incomplete story — this project adds multi-touch attribution.
:::
:::::

------------------------------------------------------------------------

## Data Overview {background-color="#2c3e50"}

::::: columns
::: {.column width="50%"}
**Source**

-   GA4 event data from BigQuery
-   Project: `odoo-487003`
-   Dataset: `analytics_523126945`

**Coverage**

-   8 snapshot days
-   Feb 9 – Apr 3, 2026
-   \~7 week span
:::

::: {.column width="50%"}
**Pipeline**

```         
BigQuery
   ↓  SQL extract
events_snapshot.csv
   ↓  Apache Arrow
events_snapshot.parquet
   ↓  R / Quarto
Analysis + Dashboard
```

**Key fields:** event name, traffic medium, device, geo, user pseudo ID
:::
:::::

------------------------------------------------------------------------

## Key Metrics at a Glance {background-color="#2c3e50"}

```{r kpi-table}
tibble::tibble(
  Metric        = c("Total Events", "Unique Users", "Page Views", "Top Channel", "Top Device"),
  Value         = c(
    scales::comma(nrow(ds)),
    scales::comma(n_distinct(ds$user_pseudo_id)),
    scales::comma(sum(ds$event_name == "page_view")),
    str_to_title(traffic_summary$medium_clean[1]),
    device_summary$device_category[1]
  )
) |>
  knitr::kable(align = c("l", "r"))
```

------------------------------------------------------------------------

## Engagement Depth

-   \~24 events per user\
-   \~7.4 page views per user

These metrics indicate that users are interacting multiple times during visits, suggesting active engagement within the snapshot.

------------------------------------------------------------------------

## Where Is Traffic Coming From? {background-color="#1a252f"}

```{r plot-traffic}
traffic_summary |>
  mutate(medium_clean = fct_reorder(medium_clean, page_views)) |>
  ggplot(aes(x = medium_clean, y = page_views, fill = medium_clean)) +
  geom_col(show.legend = FALSE, width = 0.7) +
  geom_text(aes(label = comma(page_views)), hjust = -0.15, size = 3.5, color = "white") +
  coord_flip() +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.2))) +
  scale_fill_brewer(palette = "Set2") +
  labs(x = NULL, y = "Page Views",
       caption = "Filtered to page_view events only") +
  theme_minimal(base_size = 13) +
  theme(
    panel.grid.major.y = element_blank()
  )
```

::: fragment
> Organic and Direct together dominate — the MSDM site relies heavily on brand awareness and search visibility.
:::

------------------------------------------------------------------------

## Who Is Visiting? {background-color="#1a252f"}

```{r plot-device}
device_summary |>
  ggplot(aes(x = "", y = pct_events, fill = device_category)) +
  geom_col(width = 1, color = "white") +
  coord_polar(theta = "y") +
  geom_text(
    aes(label = paste0(device_category, "\n", round(pct_events, 1), "%")),
    position = position_stack(vjust = 0.5),
    size = 5, fontface = "bold", color = "white"
  ) +
  scale_fill_brewer(palette = "Set2") +
  labs(fill = "Device") +
  theme_void(base_size = 13) +
  theme(
    panel.grid.major.y = element_blank()
  )
```

::: fragment
> Desktop dominates — typical for program research. But mobile unique users warrant continued UX investment.
:::

------------------------------------------------------------------------

## Attribution: Last-Touch vs Markov {background-color="#1a252f"}

```{r plot-attribution}
comparison |>
  tidyr::pivot_longer(cols = c(Last_Touch, Markov),
                      names_to = "Model", values_to = "value") |>
  mutate(Model = factor(Model, levels = c("Last_Touch", "Markov"))) |>
  ggplot(aes(x = Channel, y = value, fill = Model)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8),
           width = 0.7, na.rm = TRUE) +
  geom_text(
    aes(label = ifelse(is.na(value), "", paste0(round(value, 1), "%"))),
    position = position_dodge(width = 0.8),
    vjust = -0.4, size = 3, color = "white", na.rm = TRUE
  ) +
  labs(
    x = "Channel", y = "Attribution (%)", fill = "Model",
    caption = "Based on attribution_dataset.csv — 1,000 users, 100 converters"
  ) +
  scale_fill_manual(values = c("Last_Touch" = "#4E79A7", "Markov" = "#E15759")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +
  theme_minimal(base_size = 13) +
  theme(
    panel.background = element_rect(fill = "transparent", color = NA),
    plot.background  = element_rect(fill = "transparent", color = NA),
    axis.text.x = element_text(angle = 30, hjust = 1)
  )
```

## What the Models Tell Us (1/2) {background-color="#2c3e50"}

| Channel     | Last-Touch | First-Touch | Markov |
|-------------|-----------:|------------:|-------:|
| Email       |        28% |         24% |    16% |
| Direct      |        21% |          8% |    19% |
| Organic     |        19% |         20% |    19% |
| Paid Search |        16% |         20% |    17% |
| Paid Social |         6% |         23% |    14% |
| Referral    |        10% |          5% |    14% |

------------------------------------------------------------------------

## What the Models Tell Us (2/2) {background-color="#2c3e50"}

| Channel     | Insight                         |
|-------------|---------------------------------|
| Email       | Strong closer & initiator       |
| Direct      | Closing step, not a true driver |
| Organic     | Stable across all models        |
| Paid Search | Consistent contributor          |
| Paid Social | ⚠️ Undervalued by last-touch    |
| Referral    | Mid-funnel role undervalued     |

::: fragment
> **Paid Social: 6% last-touch → 23% first-touch → 14% Markov.** It starts journeys but gets no closing credit.
:::

------------------------------------------------------------------------

## Recommendations (1/2) {background-color="#2c3e50"}

::: incremental
1.  **Invest more in Paid Social** — only 6% last-touch, but 23% first-touch and 14% Markov. It initiates journeys but gets almost no closing credit.

2.  **Keep Email strong** — top in both last-touch (28%) and first-touch (24%). Best for bottom-of-funnel re-engagement.

3.  **Don't over-budget Direct** — 21% last-touch but only 8% first-touch. It's the final step, not a true driver.
:::

------------------------------------------------------------------------

## Recommendations (2/2) {background-color="#2c3e50"}

::: incremental
4.  **Invest in Referral partnerships** — Markov (14%) \> Last-Touch (10%). Meaningful mid-funnel role that position-based models miss.

5.  **Rebalance upper vs lower funnel** — shift some spend toward Paid Social and Referral while maintaining Email efficiency.
:::

------------------------------------------------------------------------

## Limitations {background-color="#2c3e50"}

::::: columns
::: {.column width="50%"}
**Data Constraints**

-   Only 8 snapshot days — trends are directional, not conclusive
-   `user_id` largely missing — no cross-device stitching
-   Nested GA4 fields excluded (`event_params`, `ecommerce`)
-   No session-level metrics
:::

::: {.column width="50%"}
**Attribution Constraints**

-   Direct traffic may mask untagged channels
-   Paid Social impressions not fully captured (walled garden)
-   Small dataset — results may shift with more data
-   No cost or ROI data to validate recommendations
:::
:::::

------------------------------------------------------------------------

## Next Steps {background-color="#2c3e50"}

::: incremental
-   **Strengthen UTM tagging** across all campaigns to reduce Direct traffic inflation
-   **Expand date coverage** — 8 days is not enough for reliable trend analysis
-   **Add cost data** — combine attribution results with spend to calculate channel ROI
-   **Test Paid Social increase** — run an experiment to validate the Markov model's findings
-   **Unpack `event_params`** — enables page-level analysis and deeper engagement metrics
:::

------------------------------------------------------------------------

## Thank You {background-color="#2c3e50"}

::::: columns
::: {.column width="60%"}
**Group 4**

-   Min Gong
-   Jeffrey Hsu
-   Emily Kuo
-   Eunice Won
-   Ceren Unal

**IBM 6530 \| May 2026**
:::

::: {.column width="40%"}
**Links**

-   📊 [Dashboard](#)
-   📄 [Full Report](#)
-   💻 [GitHub Repo](https://github.com/hsujeffrey/ibm6530-group4-project)
:::
:::::
