---
name: Eunice
surname: Won
position: "Intake Specialist & Marketing / Legal Assistant"
phone: +1 (213) 706-9999
www: ""
email: "euniceewon@gmail.com"
github: ""
linkedin: ""
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

Graduate student pursuing an M.S. in Digital Marketing with experience in legal intake, client communication, marketing coordination, and community engagement. Strong background in fast-paced client-facing environments with bilingual communication skills in English and Korean.

# Technical Skills

-   **Programming Languages:** R, SQL, etc.

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ College, ~ Institution,
  "M.S. Digital Marketing", "Expected 2026", "College of Business Administration", "California State Polytechnic University, Pomona",
  "B.A. Psychological Science; B.A. Education Sciences", "Completed", "Cum Laude", "University of California, Irvine"
) %>%
  detailed_entries(Degree, Year, College, Institution)
```

# Work Experience

```{r}
tribble(
  ~ Years, ~ Company, ~ Duties, ~ Title,

  "Oct. 2025 – Current", "Cha Cha Cha Law — Los Angeles, CA",
  list(
    "Handle client intake and communication for lemon law and personal injury matters.",
    "Coordinate case documents including repair orders, purchase agreements, and supporting records.",
    "Prepare client communications, schedule attorney calls, and assist with case updates.",
    "Support marketing initiatives and client outreach across digital platforms.",
    "Communicate professionally with clients, dealerships, and manufacturers in English and Korean."
  ),
  "Intake Specialist & Marketing / Legal Assistant",

  "Mar. 2025 – Current", "Center for Customer Insights & Digital Marketing (CCIDM) — Pomona, CA",
  list(
    "Supported engagement initiatives that increased student awareness and participation.",
    "Created social media and email campaigns for workshops and events.",
    "Collaborated with faculty and students to coordinate logistics and outreach."
  ),
  "Brand Community Engagement Specialist",

  "Jul. 2024 – Current", "6xs Coffee DTLA — Los Angeles, CA",
  list(
    "Maintained efficient customer service in a fast-paced café environment.",
    "Managed high-volume orders while ensuring accuracy and customer satisfaction."
  ),
  "Barista",

  "Mar. 2022 – Feb. 2024", "Dosol Elementary School — Daejeon, South Korea",
  list(
    "Taught English to over 700 students weekly.",
    "Designed interactive lessons and organized English Camp activities.",
    "Worked closely with Korean co-teachers on curriculum development."
  ),
  "English Teacher"
) %>%
  detailed_entries(
    what = Title,
    when = Years,
    with = Company,
    why = Duties
  )
```

# Certification & Skills

Google Analytics • Google Ads Search • Data Wrangling & Visualization • HubSpot • Canva • R Programming • Microsoft Office • Google Workspace • English (Fluent) • Korean (Fluent)
